Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-25 main.tex
Some rough intro story

\bcp{How about coining the term ``lockstep noninterference'' and then saying
that we study several variants...?}

@@

\newcommand*{\clean}{{\em clean}}
\newcommand*{\tainted}{{\em tainted}}
\newcommand*{\boring}{{\em boring}}
\begin{itemize}
\item We define three {\em tags} \leo{have we defined what these
  are?}: \clean, \tainted, and \boring. Machine components tagged
  \clean by the policy represent protected locations that should never
  be tainted. Components tagged \tainted are either sources of taint
  (e.g. network inputs) or components that have been influenced by
  other \tainted ones. Finally \boring components are locations that
  are allowed to become tainted (perhaps temporarily) but have not
  yet.
\end{itemize}

>>>>

\bcp{How about coining the term ``lockstep noninterference'' and then saying
  that we study several variants...?}
\leo{Rough story of the paper based on the discussion at POPL:}
\begin{itemize}
\item Noninterference is a desirable security property: secret information
  does not affect pulbic outputs of systems.
\item Traditionally, it is expressed as a {\em hyperproperty}, a
  property over pairs of execution traces. \leo{Two machines, differ
    secret data, run, indist}
\item The two execution traces are allowed differ arbitrarily in their
  control flow: branching on secret data can cause the machines to follow
  different execution paths.
\item \leo{Why is that bad? Hard to test/visualize? Even though interesting and permissive?}
\item \leo{Where do we mention contours, if at all?}
\item 
\item In this paper we describe a restricted form of hyperproperties:
  lockstep-hyperproperties, where the two traces execute the same
  sequence of instructions.
\item This kind of hyperproperty is still of practical interest: we
  can use it to encode both taint tracking, heap safety, and stack
  safety as noninterference properties.
\item Intuitively, taint tracking enforces noninterference until the
  program branches on tainted data. Then all bets are off.
\item On the other hand, stack safety is a monitoring policy that can
  enforce this lockstepness.
\item By restricting the class of hyperproperties we care about, we
  are also able to give a pretty extensional characterization of
  well-bracketed classification and declassification: what is
  considered secret can change throughout the execution.
\item For example, stack safety caller/callee accessible data.  
\end{itemize}

Contributions:
\begin{itemize}
\item \leo{Something about lockstep-hyperproperties as an abstraction}
\item An extensional characterization of taint tracking.
\item A novel stack safety policy and property characterized as noninterference.
\item A testing framework for testing lockstep-hyperproperties (merge with 1?)  
\end{itemize}

@@

\newcommand*{\clean}{{\em clean}}
\newcommand*{\tainted}{{\em tainted}}
\newcommand*{\boring}{{\em boring}}
\begin{itemize}
\item We define three {\em tags} \leo{have we defined what these
  are?}: \clean, \tainted, and \boring. Machine components tagged
  \clean by the policy represent protected locations that should never
  be tainted. Components tagged \tainted are either sources of taint
  (e.g. network inputs) or components that have been influenced by
  other \tainted ones. Finally \boring components are locations that
  are allowed to become tainted (perhaps temporarily) but have not
  yet.
\item To implement the taint tracking property as a policy, we
  initialize a map from components to tags. From this map, we can read
  a contour in a straightforward manner: \clean is \VIS, the other
  tags are \HID.
\end{itemize}

\leo{How do we want to write these rules? Explain .dpl?}
%//TODO: This is a bug opportunity, right?
%   // explicit failure for write tainted val to clean addr
%   storeGrp(   mem == [+Clean], addr == _, val == [+Taint], env == _
%              -> fail "Tainted data written to clean memory")
% 
%   // Propogate taint
%#ifndef ADD_NO_TAINT_1
%   ^ arithGrp(env == _, op1 == [+Taint], op2 == _ -> env = env, res = op1)
%#else
%//   ^ arithGrp(env == _, op1 == [+Taint], op2 == _ -> env = env, res = {})
%#endif
%#ifndef ADD_NO_TAINT_2
%   ^ arithGrp(env == _, op1 == _, op2 == [+Taint] -> env = env, res = op2)
%#else
%//   ^ arithGrp(env == _, op1 == _, op2 == [+Taint] -> env = env, res = {})
%#endif
%   ^ mulDivRemGrp(code == _, env == _, op1 == [+Taint], op2 == _ -> env = env, res = op1)
%   ^ mulDivRemGrp(code == _, env == _, op1 == _, op2 == [+Taint] -> env = env, res = op2)
%   ^ immArithGrp(env == _, op1 == [+Taint] -> env = env, res = op1)
%#ifndef NO_MEM_TAINT_CHECK_LOAD
%   ^ loadGrp(mem == [+Taint], addr == _, env == _ -> env = env, res = mem )
%#else
%// No mem check
%#endif
%#ifndef NO_ADDR_TAINT_CHECK_LOAD
%   ^ loadGrp(mem == _, addr == [+Taint], env == _ -> env = env, res = addr )
%#else
%// THIS WAS AN ACTUAL BUG! Addres check ommitted
%#endif
%#ifndef NO_VAL_TAINT_CHECK_STORE
%//NOT A BUG! We never write tainted data to clean memory because of the first rule
%   ^ storeGrp(mem == _, addr == _, val == [+Taint], env == _ -> env = env, mem = val)
%#else
%// NO CHECK
%#endif
%#ifndef NO_MEM_TAINT_CHECK_STORE
%   ^ storeGrp(mem == [+Taint], addr == _, val == _, env == _ -> env = env, mem = mem )
%#else
%// NO CHECK
%#endif
%#ifndef NO_ADDR_TAINT_CHECK_STORE
%   ^ storeGrp(mem == _, addr == [+Taint], val == _, env == _ ->
%     fail "Can't write through a tainted pointer")
%#else
%// Could also taint mem with addr. Also an actual bug (but one that I made).
%// THIS WAS AN ACTUAL BUG! Addres check ommitted
%#endif
%   // keep clean mem stays clean always
%   ^ storeGrp(   mem == [+Clean], addr == _, val == _, env == _ -> env = env, mem = mem)
